\textbf{Case Studies II - Community Talks}

### 2013-04-09 ricardogarfe/final_report/002-webkit-community-talk.tex
Update 002-webkit-community-talk.tex
I add bold format to all the linked text . so the reader can knew there is a link  here

\par You can see better numbers in the study by Bitergia on WebKit community posted on February 6, 2013, \href{http://blog.bitergia.com/2013/02/06/report-on-the-activity-of-companies-in-the-webkit-project/}{Bitergia blog}.

@@

\begin{itemize}
	\item Bug Traking System (BTS) Bugzilla - \url{https://bugs.webkit.org/}
	\item Issue Tracking System (ITS) Trac - \url{http://trac.webkit.org/}
	\item Early Warning Systems (EWS) Bugzilla - \url{http://webkit-commit-queue.appspot.com/}
	\item Developer Guides for each Operative System - \url{http://www.webkit.org/building/tools.html}
\end{itemize}

@@

\par As we can see, the system shows a first image of the \href{http://webkit-commit-queue.appspot.com/}{status of contributions}.

@@

\par Accessing \href{http://build.webkit.org/console}{BuildBot WebKit Console}, we have access to the results and follow-up of each of the patches and tests for each of the existing distributions (ports).

@@

\par In WebKit there are many ways of contributions; translations, code, documentation, etc. We are going to focus on contribute with code.
\par There is a guideline explaining \href{http://www.webkit.org/coding/contributing.html}{how to contribute code}. These are the steps you have to follow to contribute code in WebKit:
\begin{itemize}
	\item Choose or create a bug report to work on.
	\item Develop your changes.
	\item Make sure your changes meet the code style guidelines. The check-webkit-style script may be of help.
	\item Run the layout tests using the run-webkit-tests script and make sure they all pass. See the testing page for more information, as well as what you need to do if you've modified JavaScriptCore.
	\item Add any new files to your working directory.
	\item Prepare a change log entry. You may have to add entries to multiple ChangeLogs. The prepare-ChangeLog script will create stub entries for you. See the paragraph about ChangeLogs below.
	\item Create the patch using the svn-create-patch script.
	\item Submit your patch for review to bugs.webkit.org.
	\item Make any changes recommended by the reviewer.
	\item Once reviewed, ask someone to land your patch or mark it for automated commit.
	\item Please watch for any regressions it may have caused (hopefully none)!
\end{itemize}

>>>>

\par You can see better numbers in the study by Bitergia on WebKit community posted on February 6, 2013,\textbf{ \href{http://blog.bitergia.com/2013/02/06/report-on-the-activity-of-companies-in-the-webkit-project/}{Bitergia blog}}.

@@

\begin{itemize}
	\item Bug Tracking System (BTS) Bugzilla - \url{https://bugs.webkit.org/}
	\item Issue Tracking System (ITS) Trac - \url{http://trac.webkit.org/}
	\item Early Warning Systems (EWS) Bugzilla - \url{http://webkit-commit-queue.appspot.com/}
	\item Developer Guides for each Operative System - \url{http://www.webkit.org/building/tools.html}
\end{itemize}

@@

\par As we can see, the system shows a first image of the \textbf {\href{http://webkit-commit-queue.appspot.com/}{status of contributions}}.

@@

\par Accessing   \textbf {\href{http://build.webkit.org/console}{BuildBot WebKit Console}}, we have access to the results and follow-up of each of the patches and tests for each of the existing distributions (ports).

@@

\par In WebKit there are many ways of contributions; translations, code, documentation, etc. We are going to focus on contribute with code.
\par There is a guideline explaining  \textbf {\href{http://www.webkit.org/coding/contributing.html}{how to contribute code}}. These are the steps you have to follow to contribute code in WebKit:
\begin{itemize}
	\item Choose or create a bug report to work on.
	\item Develop your changes.
	\item Make sure your changes meet the code style guidelines. The check-webkit-style script may be of help.
	\item Run the layout tests using the run-webkit-tests script and make sure they all pass. See the testing page for more information, as well as what you need to do if you've modified JavaScriptCore.
	\item Add any new files to your working directory.
	\item Prepare a change log entry. You may have to add entries to multiple ChangeLogs. The prepare-ChangeLog script will create stub entries for you. See the paragraph about ChangeLogs below.
	\item Create the patch using the svn-create-patch script.
	\item Submit your patch for review to bugs.webkit.org.
	\item Make any changes recommended by the reviewer.
	\item Once reviewed, ask someone to land your patch or mark it for automated commit.
	\item Please watch for any regressions it may have caused (hopefully none)!
\end{itemize}
